Modal Verification Patterns for Systems

### 2025-06-25 paper.tex
i think this is ok

\subsubsection{Reference-Counting Memory Reclamation}
In a typical configuration, allocating, deallocating and referencing memory locations for client code 
leaves the memory layout in a form of DAG (directed acyclic graph) with a unique root, which resembles the first stack pointer referencing the allocated memory.
% To ease picturing the memory layout after a set of requests from the client code (for allocation, referencing etc.), we can think of the unique roots of DAGs as 
% \emph{super} block addresses -- this time multiple ones, not only two -- in Figure \ref{fig:cowindex}, 
% from which a path is created for a stack pointer reference to the allocated memory. 
\todo[inline,color=cyan]{
Why is this a DAG? Normally programs can easily create cycles, so the DAG bit requires a little more explanation.
Do we mean that it is ``often'' the case that it's a DAG?}

>>>>

\subsubsection{Reference-Counting Memory Reclamation}
In a typical configuration, allocating, deallocating and referencing memory locations for client code 
leaves the memory layout \emph{ideally} in a form of DAG (directed acyclic graph) with a unique root, which resembles the first stack pointer referencing the allocated memory. DAG abstraction instead of recursive decent tree allows non-duplication on the reference counts for the identical memory objects.
% To ease picturing the memory layout after a set of requests from the client code (for allocation, referencing etc.), we can think of the unique roots of DAGs as 
% \emph{super} block addresses -- this time multiple ones, not only two -- in Figure \ref{fig:cowindex}, 
% from which a path is created for a stack pointer reference to the allocated memory. 
\todo[inline,color=cyan]{
Why is this a DAG? Normally programs can easily create cycles, so the DAG bit requires a little more explanation.
Do we mean that it is ``often'' the case that it's a DAG?}
